---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Metas  
Metafor is meta-awesome.  
Calculating effect sizes is a good first step.    
https://www.rdocumentation.org/packages/metafor/versions/3.0-2/topics/escalc


escalc measurement argument

"MD" for the raw mean difference (e.g., Borenstein, 2009),

"SMD" for the standardized mean difference (Hedges, 1981),

"SMDH" for the standardized mean difference with heteroscedastic population variances in the two groups (Bonett, 2008, 2009),

"ROM" for the log transformed ratio of means (Hedges et al., 1999; Lajeunesse, 2011)

### Challenge 1. Restoration outcomes and species richness  
https://knb.ecoinformatics.org/view/doi%3A10.5063%2F057DCQ 

## Restoration richness tipping point analysis

Is there evidence that species richness reported predicts restoration outcomes?

### Prisma  

Terms 
2021
[restoration * desert * vegetation*]   
[restoration “agricultural lands”]   


```{r}
library(PRISMAstatement)
prisma(found = 2482,
       found_other = 0,
       no_dupes = 1841, 
       screened = 1841, 
       screen_exclusions = 313, 
       full_text = 313,
       full_text_exclusions = 251, 
       qualitative = 61, 
       quantitative = 31,
       width = 600, height = 600) #31 = plant richness, and 61 are the ag and grazing papers
```


### Data
```{r data}
#libraries
library(tidyverse)

#data
restoration <- read_csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3A168b5aeb-b110-4eb3-93d0-dea71ab34ddb"))

#%>% 
  #filter(species_richness > 0, !is.na(mean.c), !is.na(se.c), !is.na(se.t), se.t > 0) %>% 
  #select(-potential.evaporation, 3:6, -spatial.grain, -term, -outcome) %>% 
  #rename(outcome = measure.success) %>% 
  #filter(!is.na(outcome))
```

### Meta
```{r}
#metafor approach
library(metafor)
library(broom)

data <- restoration

#data <- escalc(measure = "ROM", m1i= mean.t, sd1i= se.t, n1i=n.t, m2i= mean.c, sd2i= se.c, n2i= n.c, data = #restoration,  append = TRUE)

#does restoration work
res1 <- rma(yi = yi, sei = vi, method = "ML", test = "knha", control=list(stepadj=0.5), data = data)
summary(res1)

#does active versus passive matter?
res2 <- rma(yi = yi, sei = vi, method = "ML", mods = ~paradigm -1, test = "knha", control=list(stepadj=0.5), data = data)
summary(res2)

#single model with moderators
res5 <- rma(yi = yi, sei = vi, method = "ML", mods = ~poly(log(species_richness), 2)*paradigm + outcome, test = "knha", control=list(stepadj=0.5), data = data)
summary(res5)

r5 <- tidy(res5) %>% 
  mutate(term = str_remove(term, "outcome")) %>% 
  filter(term != "intercept")

knitr::kable(r5)
#anova(res4, res5) #anova(reduced, full) to match print output order
#likelihood ratio test, the results of which we can see in the LRT

#bias
regtest(res5) 
ranktest(res5)
funnel(res5)
#permutation to assess fit
#permutest(res5, iter = 100) #success no meaningful decreases in statistical significance
## Running 100 iterations for approximate permutation test.
## 
## Test of Moderators (coefficients 2:11):
## F(df1 = 10, df2 = 327) = 6.7616, p-val* = 0.0100
## 
## Model Results:
## 
##                                                  estimate      se     tval   df 
## intrcpt                                           -0.1386  0.2048  -0.6766  327 
## poly(log(species_richness), 2)1                    2.3107  1.3517   1.7095  327 
## poly(log(species_richness), 2)2                  -10.7269  2.1718  -4.9391  327 
## paradigmpassive                                   -0.2973  0.1343  -2.2142  327 
## outcomenative communities                          0.6621  0.2080   3.1839  327 
## outcomepalatable vegetation                        0.7766  0.4513   1.7207  327 
## outcomerevegetation                                0.8193  0.2996   2.7343  327 
## outcomeseed production                             1.3194  0.3803   3.4695  327 
## outcomesoil health                                 0.6229  0.3354   1.8574  327 
## poly(log(species_richness), 2)1:paradigmpassive   -1.4690  2.6647  -0.5513  327 
## poly(log(species_richness), 2)2:paradigmpassive   11.8513  2.5214   4.7002  327 
##                                                   pval*     ci.lb    ci.ub 
## intrcpt                                          0.8600   -0.5415   0.2644     
## poly(log(species_richness), 2)1                  0.0600   -0.3484   4.9698   . 
## poly(log(species_richness), 2)2                  0.0100  -14.9994  -6.4544  ** 
## paradigmpassive                                  0.0700   -0.5614  -0.0332   . 
## outcomenative communities                        0.0100    0.2530   1.0712  ** 
## outcomepalatable vegetation                      0.1100   -0.1113   1.6644     
## outcomerevegetation                              0.0100    0.2298   1.4087  ** 
## outcomeseed production                           0.0100    0.5713   2.0675  ** 
## outcomesoil health                               0.0600   -0.0368   1.2826   . 
## poly(log(species_richness), 2)1:paradigmpassive  0.5200   -6.7111   3.7731     
## poly(log(species_richness), 2)2:paradigmpassive  0.0100    6.8910  16.8115  ** 
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

#more complex spline model for relevant fits
library(rms)
res6 <- rma(yi = yi, sei = vi, mods = ~ rcs(species_richness, 3)*paradigm, data = data)
#summary(res5)
r6 <- tidy(res6) #%>% 
  #mutate(term = str_remove(term, "outcome")) %>% 
  #filter(term != "intercept")
#r6

#knots from spline model ie thresholds
knots <- attr(rcs(model.matrix(res6)[,2], 3), "parms")
knots

```

### Viz
```{r viz}
ggplot(data, aes(species_richness, yi, weight = vi, color = paradigm)) +
  geom_point(size = 2) +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 2, se = TRUE) +
  geom_hline(yintercept = 0, linetype = 2, colour = "black", size = 1.5) +
  labs(x = "local plant species richness", y = "lrr of restoration outcomes", color = "") +
  scale_color_brewer(palette = "Set1") +
  xlim(0,100) + 
  ylim(-5, 5) +
  theme_classic() +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))
```


